Syntax and Semantics of Abstract Binding Trees

### 2015-12-04 paper.tex
Start adding summary of nominal sets, schanuel topos, proofs

@@

Going forward, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{J_\mathsf{atm}}$, where $J_\mathsf{atm}$
is the atomic coverage (sc.\ every non-empty family covers).

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets \cite{fiore-staton:2006,
  pitts:2013}; we differ only in discussing sheaves on $\SCtxSite$, as opposed
  to sheaves on $\OpCat{\SymSets}$ (i.e.\ unisorted contexts).
\end{remark}

>>>>

\DeclareMathOperator{\Perm}{\mathbf{Perm}}

@@

In the future, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{J_\mathsf{atm}}$, where $J_\mathsf{atm}$
is the atomic coverage (sc.\ every non-empty family covers).

\subsubsection{Relation to Nominal Sets and the Schanuel Topos}

Pitts defines a category $\mathbf{Nom}$ of nominal sets in \cite{pitts:2013}
which function equivalently to the sheaves that we considered above, in the
case of $\IMode{\Sorts}\cong\IMode{\mathbb{1}}$. Fix a countably infinite set
of atoms $\mathbb{A}$; then let $\Perm\mathbb{A}$ be the group of permutations
(i.e.\ autoequivalences) on $\mathbb{A}$.  Considered as a category,
$\Perm\mathbb{A}$ has a single object $\bullet$ with morphisms
$\Of{\pi}{\bullet\ra\bullet}$ for each $\Member{\pi}{\Dom{\Perm\mathbb{A}}}$.
Then, the category of nominal sets $\mathbf{Nom}$ is the subcategory of
$\Sets^{\Perm\mathbb{A}}$ containing just the presheaves which satisfy a
\emph{finite support} condition analogous to the one that we have formulated
above.\todo[inline]{write it out}

The category $\mathbf{Nom}$ is equivalent to the category of covariant sheaves
on $\SymSets$ under the atomic coverage, called the Schanuel Topos
$\Define{\mathbb{S}}{\Sheaves{\OpCat{\SymSets}}}$ \cite{pitts:2013,
fiore-staton:2006}; equivalently, the Schanuel topos is the subcategory of
$\Sets^\SymSets$ containing only pullbacks-preserving functors.

In addition to the unisorted nominal sets framework, Pitts also briefly
discusses a multi-sorted version of the apparatus in which the countably
infinite set of atoms $\mathbb{A}$ is equipped with a sort assignment
$\Of{\mathfrak{s}}{\mathbb{A}\to\Sorts}$ such that all the fibres of
$\mathfrak{s}$ are countably infinite; then, he defines for any such assignment
the category $\mathbf{Nom}_\mathfrak{s}$ of $\mathfrak{s}$-sorted nominal sets
as the category of presheaves on the group of $\mathfrak{s}$-respecting
permutations on $\mathbb{A}$, $\Perm_\mathfrak{s}\mathbb{A}$.

In the same way as the Schanuel topos is equivalent to the unisorted nominal
sets, we expect to find an equivalence between $\Sheaves{\SCtxSite}$ and the
limit $\int_{\mathfrak{s}}\mathbf{Nom}_\mathfrak{s}$. At the very least,
the sheaf topos $\Sheaves{\SCtxSite}$ may serve as a multi-sorted
generalization of the Schanuel topos, for which we may carry over certain
useful results, including its characterization as the subcategory of
$\Sets^\SCtx$ which contains just the pullbacks-preserving functors.

\begin{thm}
  A presheaf $\Of{X}{\Sets^{\SCtx}}$ is a sheaf on $\SCtxSite$ just when it
  preserves pullbacks.
\end{thm}

\begin{proof}

  The proof is essentially the same as that of the analogous lemma for the
  Schanuel topos as presented in \cite[A.2.1.11.h]{johnstone:2002}, but we will
  give a slightly more detailed version here. The presheaf $X$ is a sheaf on the
  atomic site $\SCtxSite$ just when, for any renaming
  $\Of{\varrho}{C\inj D}$ and any $\Member{n}{X(D)}$ if
  $\IsEq{n\varrho_0}{n\varrho_1}$ for all diagrams
  \[
    \begin{tikzcd}[sep=large]
      \IMode{C} \arrow[r, hook, "\IMode{\varrho}"] &
      \IMode{D}
        \arrow[r, hook, shift left, "\IMode{\varrho_0}"]
        \arrow[r, hook, swap, shift right, "\IMode{\varrho_1}"]
      &
      \IMode{E}
    \end{tikzcd}
  \]
  such that $\IsEq{\varrho_0\circ\varrho}{\varrho_1\circ\varrho}$, then there
  exists a unique $\Member{m}{X(C)}$ such that $\IsEq{m\varrho}{n}$. In other
  words, the arrow $X(\varrho)$ is an equalizer, as in the following:
  \[
    \begin{tikzcd}[sep=large]
      \IMode{X(C)} \arrow[r, "\IMode{X(\varrho)}"] &
      \IMode{X(D)}
        \arrow[r, shift left, "\IMode{X(\varrho_0)}"]
        \arrow[r, swap, shift right, "\IMode{X(\varrho_1)}"]&
      \IMode{X(E)}
      \\
      \IMode{\mathbb{1}}
        \arrow[u, densely dotted, "\OMode{m}"]
        \arrow[ur, "\IMode{n}"]
    \end{tikzcd}
  \]

  Now, because $\Sets$ is a regular category, $X(\varrho)$ is an equalizer
  precisely when it is a monomorphism. Therefore, if we have assumed that $X$
  preserves pullbacks, in order to demonstrate that $X$ is a sheaf, it suffices
  to show that $X(\varrho)$ is monic. If $X$ preserves pullbacks, then it also
  preserves monomorphisms, because in any category with pullbacks, $\Of{f}{A\ra
  B}$ is monic just when the square
  \[
    \begin{tikzcd}[sep=large]
      \IMode{A}
        \arrow[r, "\IMode{\ArrId{A}}"]
        \arrow[d, "\IMode{\ArrId{A}}"] &
      \IMode{A} \arrow[d, "\IMode{f}"]\\
      \IMode{A} \arrow[r, "\IMode{f}"] &
      \IMode{B}
    \end{tikzcd}
  \]
  is a pullback. Because $X$ preserves monomorphisms, and all arrows in $\SCtx$
  are monic, then $X(\varrho)$ is monic. Hence, $X$ is a sheaf.

  \todo[inline]{prove the other direction}

\end{proof}
